Project Report

### 2022-05-09 project_discussion_report/main.tex
Fixed typos, improved sentences

    Our hyperparameters were chosen through manual trial-and-error. We did not implement
    any regularization techniques, nor did we use our validation set or cross validation to tune 
    any hyperparameters. All of our results for our different model architectures were generating
    high accuracy (>98\%) on our single de novo sequence. In the future, we would like to experiment
    more with tuning hyperparameters in particular if the task becomes harder for different starting
    de novo sequences and therefore different training datasets. Table~\ref{tab:hyperparameters}
    displays our chosen hyperparameters.

@@

  \subsection{Predictions on De Novo Sequence}
    To perform the task of deploying our models to predict gaps in our de novo sequence, 
    we trained two models: one to learn the dependencies in the forward direction and
    one to learn the dependencies in the reverse direction. This was necessary to deploy 
    our models to predict gaps in the beginning or end of the target sequence. 
    For example, if our target sequence begins with "DIQMSP" and we want to predict "DIQ", then
    we cannot predict from the forward direction, since "DIQ" is the absolute start of 
    the sequence. We must therefore be able to predict "DIQ" given the sequence
    ahead of it. Similarly, we must predict in the forward direction for gaps at the absolute end of the sequence.

>>>>

    Our hyperparameters were chosen through manual trial-and-error. We did not implement
    any regularization techniques, nor did we use our validation set or cross validation to tune 
    any hyperparameters. All of our results for our different model architectures were generating
    high accuracy (98-99\%) on our single de novo sequence. Table~\ref{tab:hyperparameters}
    displays our chosen hyperparameters.

@@

  \subsection{Predictions on De Novo Sequence}
    To deploy our models to predict gaps in our de novo sequence, 
    we trained two models: one to learn the dependencies in the forward direction and
    one to learn the dependencies in the reverse direction. This was necessary to predict 
    gaps in the beginning or end of the target sequence. 
    For example, if our target sequence begins with "DIQMSP" and we want to predict "DIQ", then
    we cannot predict from the forward direction, since "DIQ" is the absolute start of 
    the sequence. We must therefore be able to predict "DIQ" given the sequence
    ahead of it. Similarly, we must predict in the forward direction for gaps at the absolute end of the sequence.
